Democracy, Public Support, and Measurement Uncertainty

### 2021-07-20 paper/dcpo_demsupport.Rmd
label and output corrected

```{r coefName-APSR, eval=TRUE}
index_coefName <- c(
    `plm::lag(SupDem_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(SupDem_trim, 1:2)2` = "Support[t-2]",
    `plm::lag(theta_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(theta_trim, 1:2)2` = "Support[t-2]",
    `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `diff(Vdem_libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
    `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",
    `diff(Liberal_z, lag = 1)` = "Delta~Support(demo~only)",
    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Support(demo~only)",
    `plm::lag(Liberal_z, 1)` = "Support[t-1](demo~only)",
    `plm::lag(Vdem_liberal_z, 1)` = "Support[t-1](demo~only)",
    `diff(Polyarchy_z, lag = 1)` = "Delta~Support(auto~only)",
    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Support(auto~only)",
    `plm::lag(Polyarchy_z, 1)` = "Support[t-1](auto~only)",
    `plm::lag(Vdem_polyarchy_z, 1)` = "Support[t-1](auto~only)",
    `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `diff(lg_imp_mdpgdp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `plm::lag(lnGDP_imp, 1)` = "Log~GDP[t-1]",
    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]",
    `diff(Corrup_TI_z, lag = 1)`= "Delta~Corruption",
    `plm::lag(Corrup_TI_z, 1)` = "Log~Corruption[t-1]",
    `Corrup_TI_z` = "Log~Corruption[t-1]"
)
```

@@

result_apsrRegime <-
  list(result_clsAPSR,
       result_pureAPSR,
       result_expAPSR) %>%
  map2_df(type_model, ~ {
    .x$`pooled-regime1`[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Regime Specified")

df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>% 
    mutate(term = index_coefName[term],
           term = factor(term, levels = unique(index_coefName)))

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: The Change of Public Support for Democracy") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
    # Using expressions of underscore and greek letters
    # scale_color_gb(palette = "digitMixed") +
    facet_wrap( ~ type)

@@

```{r num-labelAJPS}
names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
)
```

```{r num-pointAJPS, results='asis'}
tb_result_cls <- map(result_clsAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-pureAJPS, results='asis'}
tb_result_pureAJPS <- map(result_pureAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-expAJPS, results='asis'}
tb_result_expAJPS <- map(result_expAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-labelAPSR}
names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
  "Corrup_TI_z" = "Corruption\n (Difference)",
  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
)
```

```{r num-pointAPSR, results='asis'}
tb_result_clsAPSR <- map(result_clsAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

```{r num-pureAPSR, results='asis'}
tb_result_pureAPSR <- map(result_pureAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

```{r num-expAPSR, results='asis'}
tb_result_expAPSR <- map(result_expAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

\begin{equation}
\mathcal{L}(\theta|y, x^{obs}) \propto \int\limit_{\chi} p(x|y, \theta)p(y|\theta)dx^{mis}.
\end{equation}

@@

\begin{equation}
\mathcal{L}(\theta|y, x) \propto \int\limit_{\chi} p(\theta|y, x)p(x|w)dx.
\end{equation}

@@

```{r moc-estimates}

@@

```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}

@@

```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=7, fig.height=10}

>>>>

```{r coefName-APSR, eval=TRUE}
index_coefName <- c(
    `plm::lag(SupDem_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(SupDem_trim, 1:2)2` = "Support[t-2]",
    `plm::lag(theta_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(theta_trim, 1:2)2` = "Support[t-2]",
    `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `diff(Vdem_libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
    `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",
    `diff(Liberal_z, lag = 1)` = "Delta~Support(electoral)",
    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Support(electoral)",
    `plm::lag(Liberal_z, 1)` = "Support[t-1](electoral)",
    `plm::lag(Vdem_liberal_z, 1)` = "Support[t-1](electoral)",
    `diff(Polyarchy_z, lag = 1)` = "Delta~Support(minoritarian)",
    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Support(minoritarian)",
    `plm::lag(Polyarchy_z, 1)` = "Support[t-1](minoritarian)",
    `plm::lag(Vdem_polyarchy_z, 1)` = "Support[t-1](minoritarian)",
    `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `diff(lg_imp_mdpgdp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `plm::lag(lnGDP_imp, 1)` = "Log~GDP[t-1]",
    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]"
    # `diff(Corrup_TI_z, lag = 1)`= "Delta~Corruption",
    # `plm::lag(Corrup_TI_z, 1)` = "Log~Corruption[t-1]",
    # `Corrup_TI_z` = "Log~Corruption[t-1]"
)
```

@@

result_apsrRegime <-
  list(result_clsAPSR,
       result_pureAPSR,
       result_expAPSR) %>%
  map2_df(type_model, ~ {
    .x$`pooled-regime1`[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Institution Specified")

df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>% 
    mutate(term = index_coefName[term],
           term = factor(term, levels = unique(index_coefName)), 
           type = factor(type, levels = c("Pooled", "Institution Specified")))

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    ggtitle("DV: The Change of Public Support for Democracy") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    facet_wrap( ~ type) + 
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term))))
    # Using expressions of underscore and greek letters
    # scale_color_gb(palette = "digitMixed")

@@

```{r num-labelAJPS, eval=TRUE}
names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
)
```

```{r num-pointAJPS, results='asis', eval=TRUE}
tb_result_cls <- map(result_clsAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-pureAJPS, results='asis', eval=TRUE}
tb_result_pureAJPS <- map(result_pureAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-expAJPS, results='asis', eval=TRUE}
tb_result_expAJPS <- map(result_expAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-labelAPSR, eval=TRUE}
names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
  "Corrup_TI_z" = "Corruption\n (Difference)",
  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
)
```

```{r num-pointAPSR, results='asis', eval=TRUE}
tb_result_clsAPSR <- map(result_clsAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

```{r num-pureAPSR, results='asis', eval=TRUE}
tb_result_pureAPSR <- map(result_pureAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

```{r num-expAPSR, results='asis', eval=TRUE}
tb_result_expAPSR <- map(result_expAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

\begin{equation}
\mathcal{L}(\theta|y, x^{obs}) \propto \int_{\chi} p(x|y, \theta)p(y|\theta)dx^{mis}.
\end{equation}

@@

\begin{equation}
\mathcal{L}(\theta|y, x) \propto \int_{\chi} p(\theta|y,x)p(x|w)dx.
\end{equation}

@@

```{r moc-estimates, eval=TRUE}

@@

```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10, eval=TRUE}

@@

```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=7, fig.height=10, eval=TRUE}
